---
title: "Statistical Inference Project"
output: html_document
---
```{r Global_options, echo=FALSE}
        library(knitr)
        library(ggplot2)
        set.seed(123)
        opts_chunk$set(echo = FALSE) 
setwd("D:/COURSES/Coursera/06_Statistical Inference/Project")
```
###PART 2: Analysis of the ToothGrowth data

##### 2.1 Load the ToothGrowth data and perform some basic exploratory data analyses
```{r, fig.width=6, fig.height=3, fig.align='center'}
data(ToothGrowth)
boxplot(len ~ supp * dose, data=ToothGrowth, ylab="Tooth Length", main="Boxplot of Tooth Growth Data")
```
As we can see on the boxplot, on average the length of the tooth increases as the dose also increases. 60 patients received two kinds of supplement in dose varying from Min. : 0.5 to Max. : 2

##### 2.2 Provide a basic summary of the data
```{r}
head(ToothGrowth)
```
ToothGrowth has 60 observations of 3 variables: `r names(ToothGrowth)`.
A summary of the data is as follow:
```{r}
summary(ToothGrowth)
```

##### 2.3 Use confidence intervals and hypothesis tests to compare tooth growth by supp and dose.
The number of sample is not big enough to apply the CLT. The following analysis assume Normal distribution of the data in order to generate confidence intervals and perform t-tests.

It is intended to study whether the means of the two groups are equal to each other. 
-The null hypothesis is that the two means are equal.
-The alternative is that they are different.
* At dose 0.5mg 
```{r}
t.test(len~supp, paired=FALSE, var.equal=FALSE, subset=ToothGrowth$dose==0.5, data=ToothGrowth)
```
* At dose 1mg 
```{r}
t.test(len~supp, paired=FALSE, var.equal=FALSE, subset=ToothGrowth$dose==1, data=ToothGrowth)
```
* At dose 2mg 
```{r}
t.test(len~supp, paired=FALSE, var.equal=FALSE, subset=ToothGrowth$dose==2, data=ToothGrowth)
```

##### 2.4 State your conclusions and the assumptions needed for your conclusions. 
An inference analysis was carried out on ToothCrowth data-set. The method selected to infere this conclusion was T-test analysis for the various dosasges levels.

###### 2.4.1 there was a significant difference in average tooth length, depending upon the dosage, the higher the supplement dosage, the longer the tooth

###### 2.4.2 For dosage levels 0.5mg and 1mg, there's a significant greater effect for OJ than VC on tooth growth length.

###### 2.4.3 For dosage level 2mg, there is no difference in effect of tooth growth length by OJ and VC.
