---
title: "Statistical Inference Project"
output: html_document
---
```{r Global_options, echo=FALSE}
        library(knitr)
        library(ggplot2)
        set.seed(123)
        opts_chunk$set(echo = FALSE) 
setwd("D:/COURSES/Coursera/06_Statistical Inference/Project")
```
###PART 1: Simulation exercise
In this simulation, you will investigate the distribution of averages of 40 exponential(0.2)s

#### Generating exponential distributed data
$$\lambda = 0.2, \, \mu = 1/\lambda, \, sd= 1/\lambda$$

It is required to generate 1000 simulation of means of 40 random variables:
```{r, fig.width=6, fig.height=3, fig.align='center'}
lambda <- 0.2
nsim <- 1000
n <- 40


data <- data.frame(mean = numeric(nsim), sd = numeric(nsim))
for (i in 1:nsim) 
        {
            data.sim <- rexp(n, lambda)
            data[i, "mean"] <- mean(data.sim)
            data[i, "sd"] <- sd(data.sim)
         }
```

##### 1.1. Show where the distribution is centered at and compare it to the theoretical center of the distribution

```{r, fig.width=6, fig.height=3, fig.align='center'}
# Define the ggplot parameter
g <- ggplot(data, aes(x = mean)) + geom_histogram(alpha = 0.5, binwidth = 0.4, aes(y = ..density..))
# formating and labeling
g <- g + labs(title = "Exponentially distributed Simulated data",
              xlab("Sample Mean values"),
              ylab("Density"))

# Plot the theoretical center of the distribution
g <- g + geom_vline(xintercept = 1/lambda, color = "black")
print(g)
```
From the plot it's possible to see that our simulated data is centered at `r round(mean(data$mean),2)` and theoretically it should be at $\mu = 1/\lambda = 5$

##### 1.2. Show how variable it is and compare it to the theoretical variance of the distribution.

```{r, fig.width=6, fig.height=3, fig.align='center'}
# histogram for the standard deviation
g <- ggplot(data, aes(x = sd)) + geom_histogram(alpha = 0.5, binwidth = 0.4, 
    aes(y = ..density..))
# formating and labeling
g <- g + labs(title = "Exponentially distributed Simulated data",
              xlab("Sample Variance"),
              ylab("Density"))
# Plot the theoretical center of the distribution
g <- g + geom_vline(xintercept = 1/lambda, color = "black")
print(g)
```
From the plot it's possible to see that the distribution of the *Sample Variance* is positively skewed

##### 1.3. Show that the distribution is approximately normal.

```{r, fig.width=6, fig.height=3, fig.align='center'}
data.scaled <- data.frame(scale(data))

g <- ggplot(data.scaled, aes(x = mean)) + geom_histogram(alpha = 0.5, binwidth = 0.4, aes(y = ..density..))
# formating and labeling
g <- g + labs(title = "Exponentially distributed Simulated data",
              xlab("Sample Mean values"),
              ylab("Density"))
# empirical density
g <- g + geom_density(aes(x=mean))
# normal density
g <- g + stat_function(fun = dnorm, color = "blue")

print(g)
```
As it is possible to appreciate on the plot the empirical distribution (black) is approximately normal (in blue)

##### 1.4. Evaluate the coverage of the confidence interval for $1/ \lambda$: $\overline{X} \pm 1.96 * S/\sqrt{n}$

```{r, fig.width=6, fig.height=3, fig.align='center'}
## Generate a simulation of confidence interval coverage
sample.sizes <- seq(10, 1000, by = 10)
coverage <- sapply(sample.sizes, function(n) {
    lhats <- rexp(n, lambda)
    xbar <- mean(lhats)
    sd <- sd(lhats)
    ll <- lhats - 1.96 * sd/sqrt(n)
    ul <- lhats + 1.96 * sd/sqrt(n)
    mean(ll < 1/lambda & ul > 1/lambda)
})
# Invert coverage to show percentages
coverage <- 1 - coverage

g <- ggplot(data.frame(sample.sizes, coverage), aes(x = sample.sizes, y = coverage)) + 
    geom_line(size = 1) + geom_hline(yintercept = 0.95, color = "red", alpha = 0.5) + 
    ylim(0.5, 1) + labs(title = "Coverage of the confidence interval", x = "Sample Sizes", y = "Coverage")

print(g)
```
Varying the number of samples, it is represented in this plot the 95% of confidence bounds.

#### For a sample size greater than 750 our confidence interval coverage is reliable


